An upper bound to gas storage and delivery via pressure-swing adsorption in porous materials

### 2021-03-09 gas-adsorption/rsc-gas-ads-complete.tex
create new flexible MOF figure
start on flexible two-state model

\begin{align}
    |n(p_{hi})\V| &> |\Delta F| \\
    |n(p_{lo})\V| &< |\Delta F|
\end{align}
This means that for a given $\Delta F$ we can put an upper bound on the
deliverable capacity.

>>>>

\begin{align}
    V_{\text{open}}|n(p_{hi})\V| &> |\Delta F| \\
    V_{\text{open}}|n(p_{lo})\V| &< |\Delta F|
\end{align}
This means that for a given $\Delta F$ we can put an upper bound on the
deliverable capacity.

\davidsays{This means we should pick the $\V$ to be big enough to make us just
on the boundary of not collapsing.  This means that:}
\begin{align}
    n(\mu_{lo} + \V)\V = \Delta F
\end{align}
This is a nonlinear equation that we want to solve.

\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{methane-298-flexible}
    \caption{Deliverable capacity of methane in a flexible substrate at 298\ K as a function of the free energy difference 
      between open and closed phases. The experimental deliverable capacity for Co(bdp) is shown for
       comparison~\cite{fixme}, along with the free energy difference between open and closed conformations~\cite{fixthis}.}
    \label{fig:methane-flexible}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{hydrogen-298-flexible}
    \caption{Deliverable capacity of hydrogen in a flexible substrate at 298\ K as a function of the free energy difference 
      between open and closed phases.}
    \label{fig:hydrogen-flexible}
\end{figure}
